Summary of the things that I learned

### 2024-10-22 200-category-theory.tex
Improve another couple of citations

  Conversely, for all $ Y: \C $ and $ X: \D $, every bijection
  \[ \C(Y, Z) \cong \D(X, F(Z)) \]
  that is natural in $ Z $ arises in this way from some universal arrow $ f: \D(X, F(Y)) $.
\end{lemma}
\begin{proof}
  See \autocite{MacLane}, Chapter III.2, Proposition 1.
\end{proof}

@@

Lastly, one can construct an adjunction using universal arrows. This lends itself particularly well for a formalization, where it is often preferable to have as few `demonstranda' as possible:
\begin{lemma}
  One can construct an adjunction $ (L, R, \eta, \epsilon) $ as above from only the functor $ L: \C \to \D $ and, for each $ X: \C $, a universal arrow $ (R(X), \epsilon_X) $ from $ L $ to $ X $.
\end{lemma}
\begin{proof}
  See \autocite{MacLane}, Chapter IV.1, Theorem 2 (iv).
\end{proof}

@@

\begin{lemma}
  The Yoneda embedding preserves limits.
\end{lemma}
\begin{proof}
  See \autocite{borceux}, Volume 1, Proposition 2.15.5 for the full proof, but note that for binary products, we have bijections
  \[ \yo(X \times Y)(Z) \xrightarrow \sim \yo(X)(Z) \times \yo(Y)(Z) \]
  sending $ f : \C(Z, X \times Y) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : \C(Z, X) \times \C(Z, Y) $ to the product morphism $ \langle g_1, g_2 \rangle : \yo(Z, X \times Y) $. This idea is also the core of the proof about general limits.
\end{proof}

@@

\begin{lemma}\label{lem:delta-exponentials}
  $ \Delta_X $ preserves exponential objects:
\end{lemma}
\begin{proof}
  See \autocite{borceux}, Volume 3, Lemma 5.8.2. This lemma shows this via the following equivalences:
  \begin{align*}
    (\C \downarrow X)((W, f), \Delta_X Y^Z) &\cong \C(W, Y^Z)\\
    &\cong \C(W \times Z, Y)\\
    &\cong (\C \downarrow X)((W \times (X \times Z), \langle f, p_1 \rangle), \Delta_X Y)\\
    &\cong (\C \downarrow X)((W, f) \times \Delta_X Z, \Delta_X Y)\\
  \end{align*}
\end{proof}

>>>>

  Conversely, for all $ Y: \C $ and $ X: \D $, every bijection
  \[ \C(Y, Z) \cong \D(X, F(Z)) \]
  that is natural in $ Z $ arises in this way from some universal arrow $ f: \D(X, F(Y)) $.
\end{lemma}
\begin{proof}
  See \autocite[][Chapter III.2, Proposition 1]{MacLane}.
\end{proof}

@@

Lastly, one can construct an adjunction using universal arrows. This lends itself particularly well for a formalization, where it is often preferable to have as few `demonstranda' as possible:
\begin{lemma}
  One can construct an adjunction $ (L, R, \eta, \epsilon) $ as above from only the functor $ L: \C \to \D $ and, for each $ X: \C $, a universal arrow $ (R(X), \epsilon_X) $ from $ L $ to $ X $.
\end{lemma}
\begin{proof}
  See \autocite[][Chapter IV.1, Theorem 2 (iv)]{MacLane}.
\end{proof}

@@

\begin{lemma}
  The Yoneda embedding preserves limits.
\end{lemma}
\begin{proof}
  See \autocite[][Volume 1, Proposition 2.15.5]{borceux} for the full proof, but note that for binary products, we have bijections
  \[ \yo(X \times Y)(Z) \xrightarrow \sim \yo(X)(Z) \times \yo(Y)(Z) \]
  sending $ f : \C(Z, X \times Y) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : \C(Z, X) \times \C(Z, Y) $ to the product morphism $ \langle g_1, g_2 \rangle : \yo(Z, X \times Y) $. This idea is also the core of the proof about general limits.
\end{proof}

@@

\begin{lemma}\label{lem:delta-exponentials}
  $ \Delta_X $ preserves exponential objects:
\end{lemma}
\begin{proof}
  See \autocite[][Volume 3, Lemma 5.8.2]{borceux}. There, the following equivalences are used for the proof:
  \begin{align*}
    (\C \downarrow X)((W, f), \Delta_X Y^Z) &\cong \C(W, Y^Z)\\
    &\cong \C(W \times Z, Y)\\
    &\cong (\C \downarrow X)((W \times (X \times Z), \langle f, p_1 \rangle), \Delta_X Y)\\
    &\cong (\C \downarrow X)((W, f) \times \Delta_X Z, \Delta_X Y)\\
  \end{align*}
\end{proof}
